\papertitle

### 2021-03-12 source_separation/paper/paper.tex
added items 3 and 4 from TODO

			\subsubsection{Universal sound separation}
			\textbf{Non-negative matrix factorization}~\cite{Cichocki_NMF, Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

@@

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. When training data for a particular problem is scarce, it is logical that unsupervised methods will perform well, as they require less data than supervised methods. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.

>>>>

			\subsubsection{Universal sound separation}
			\textbf{Non-negative matrix factorization}~\cite{Cichocki_NMF, Fevotte_NMF} is an unsupervised learning method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

@@

	Furthermore, the one unsupervised method we tested, NMF, outperformed all the supervised methods. This suggests that methods like NMF can still be useful for specific problems when available data is limited. When training data for a particular problem is scarce, it is logical that unsupervised methods will perform well, as they require less data than supervised methods. The NMF also outperformed the ground truth orchestrations, which could be due to the relative simplicity of NMF's output subtargets making subsequent orchestration easier for Orchidea, but more experimentation would need to be done in order to confirm this. It is important to notice that for the supervised methods, we used pre-trained versions of the neural models. All of these models, except for TDCN++, were trained on musical data. However, we tested them on a wide range of targets, many of which were not strictly musical. This could explain why Demucs, Open-Unmix, and TDCN performed worse than NMF, and why TDCN++, which was trained on arbitrary sounds, outperformed the other supervised methods. Therefore, we may infer from our results that models trained on generic sounds generate a better separation for orchestration when compared to models trained only on musical sounds.
